Concurrent Programming with Harmony

### 2020-07-30 book/paper.tex
Latest
Made pass over Chapter 12

\section*{Exercises}
\begin{problems}
\item
Run \autoref{fig:incfixed} using (i) \texttt{synch}, and (ii), \texttt{synchS}.
Report how many states were explored by Harmony for each module.
\item \label{ex:trylock} Implement \texttt{trylock}(\textit{lk}) as an additional
interface for both the \texttt{synch} and \texttt{synchS} modules.
This interface is like \texttt{lock}(\textit{lk}) but never blocks.  It
returns \texttt{True} if the lock was available (and now acquired) or \texttt{False}
if the lock was already taken.
Hint: you do not have to change the existing code.
\end{problems}

@@

Consider the following synchronization problem that we call
\emph{Italian Philosophers} (a simplification of
the famous Dining Philosophers problem described in \autoref{ch:deadlock}).
There are five philosophers sitting around a table, each with a plate of
spaghetti in front of them.
There is a glass sitting in the middle of the table with only
three forks in it.  A philosopher needs one of those forks to eat, but clearly,
no more than three philosophers can eat at a time.
But a lock can only count to one.

@@

\section*{Exercices}
\begin{problems}
\item Add an assertion that demonstrates that at most three
Italian philosophers are eating at the same time?
\item Implement a test program that checks to see that
the solution allows more than one Italian philosopher to eat at the same time?
\item \label{ex:qsort}
\autoref{fig:qsort} shows an iterative implementation of the Qsort
algorithm, and \autoref{fig:qsorttest} an accompanying test program.
The array to be sorted is stored in  shared variable $a$.
Another shared variable, \textit{todo}, contains the ranges of the
array that need to be sorted (initially the entire array).
Re-using as much of this code as you can, implement a parallel version of
this.  You should not have to change the methods \texttt{swap}, \texttt{partition},
or \texttt{sortrange} for this.  Create \texttt{NWORKERS} ``worker processes''
that should replace the \texttt{qsort} code.  Each worker loops until \textit{todo}
is empty and sorts the ranges that it finds until then.  The \texttt{main}
process needs to wait until all workers are done.  Use a semaphore for this:
the \texttt{main} process should use \texttt{P} to wait for each
worker to terminate.  After that it should check that the array is sorted and
that it is a permutation of the original array.
\end{problems}

>>>>

\section*{Exercises}
\begin{problems}
\item
Run \autoref{fig:incfixed} using (i) \texttt{synch} and (ii) \texttt{synchS}.
Report how many states were explored by Harmony for each module.
\item \label{ex:trylock} Implement \texttt{trylock}(\textit{lk}) as an additional
interface for both the \texttt{synch} and \texttt{synchS} modules.
This interface is like \texttt{lock}(\textit{lk}) but never blocks.  It
returns \texttt{True} if the lock was available (and now acquired) or \texttt{False}
if the lock was already taken.
Hint: you do not have to change the existing code.
\end{problems}

@@

Consider the following synchronization problem that we call
\emph{Italian Philosophers} (a simplification of
the famous Dining Philosophers problem described in \autoref{ch:deadlock}).
There are five philosophers sitting around a table, each with a plate of
spaghetti in front of them.
There is a glass sitting in the middle of the table with only
three forks in it.  A philosopher needs one of those forks to eat, but clearly,
no more than three philosophers can eat at a time.
Unfortunately, a lock can only count to one.

@@

\section*{Exercices}
\begin{problems}
\item How might you check with Harmony that at most three
Italian philosophers can eat at the same time?
\item Implement a test program that checks to see that
the solution allows more than one Italian philosopher to eat at the same time?
\item \label{ex:qsort}
\autoref{fig:qsort} shows an iterative implementation of the Qsort
algorithm, and \autoref{fig:qsorttest} an accompanying test program.
The array to be sorted is stored in  shared variable $a$.
Another shared variable, \textit{todo}, contains the ranges of the
array that need to be sorted (initially the entire array).
Re-using as much of this code as you can, implement a parallel version of
this.  You should not have to change the methods \texttt{swap}, \texttt{partition},
or \texttt{sortrange} for this.  Create \texttt{NWORKERS} ``worker processes''
that should replace the \texttt{qsort} code.  Each worker loops until \textit{todo}
is empty and sorts the ranges that it finds until then.  The \texttt{main}
process needs to wait until all workers are done.  Use a semaphore for this:
the \texttt{main} process should use \texttt{P} to wait for each
worker to terminate.  After that it should check that the array is sorted and
that it is a permutation of the original array.
\end{problems}
